Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-01-02 automatica/paper.tex
reviewed Description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Our benchmark suite consists of 18 MIMO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
these models are discretized with different sample times, which thus results in $167$ benchmarks
to evaluate our proposal approach.

The DC motor benchmark describes the velocity dynamics of a basic 
brushed direct current electrical machine. The automotive cruise control system 
benchmark is used to keep constant the speed of an automobile, 
tracking a desired speed reference, compensating disturbances and 
uncertainties related to relief and terrain.The pendulum benchmark consists of a swinging point mass suspended from 
a frictionless pivot through a negligible mass rod, while the inverted pendulum 
benchmark is a system similar to the pendulum, but the point 
mass must be equilibrated above the pivot point, which is mounted on an 
one degree of freedom cart that moves over a track through a DC motor.

The magnetic suspension benchmark corresponds to the discrete model of a 
simple eletromagnet-ball system, where a steel ball is levitated in air 
by the action of an electromagnetic force generated by an electromagnet.
The magnetic pointer benchmark is a pointer usually employed in analogue 
gauges and indicators, whose angular position dynamics is controlled 
by a magnetic field. The 1/4 Car Suspension benchmark corresponds to the model of a single 
wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
of a mass springer damp model, which connects the car to one of its wheels.

The Computer Tape Driver benchmark is a computer storage device used to read and write 
data on magnetic tapes. The Acrobot benchmark corresponds to the model of a two-link 
underactuated robot manipulator, named Acrobot, linearized by partial 
feedback linearization~\cite{acrobot}. The high-order system benchmarks correspond to a series of high-order control system model 
generally used as example for order reduction techniques~\cite{CHEN1979389}.
Here, these benchmarks are used to evaluate the proposed control 
synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
to be considered.

The Continuous Stirred Tank Reactor benchmark describes a linear model for PH dynamics of a PH 
neutralization process of an aqueous solution of sodium acetate with 
hydrochloric acid in a continuous flow stirred-tank reactor. The Flexible Beam benchmark is a plant 
usually employed in vibration studies; it consists of a flexible metallic structure with piezoceramic actuators and sensors.
The Helicopter Longitudinal Motion benchmark describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.
The USCG cutter Tampa Heading Angle benchmark describes the heading angle 
dynamics of a Coast Guard cutter. The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
of a linear model of a synchronous machine connected to an  infinite bus.

The Guidance Control System benchmark is another high-order system 
model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
techniques. Guidance systems are used to determine the path of an 
autonomous vehicle movement.

The Satellite Attitude Control System benchmark describes the dynamics of a satellite attitude, 
{\it i.e.}, the orientation angles. An attitude control system must 
maintain the desired orientation of satellite with respect to an 
inertial frame during all the excursion. The springer-mass damper system benchmarks 
are classic models for several mechanical systems dynamics. These benchmarks describe a mass,
which is fixed to a node by means of a springer and moves under the action of a 
input force, damping, and elastic force.

>>>>

Our benchmark suite consists of 18 MIMO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS};
these models are discretized with different sample times, which thus leads to $167$ different benchmarks
to evaluate our proposal approach.

The DC motor benchmark describes the velocity dynamics of a basic 
brushed direct current electrical machine. The automotive cruise control system 
benchmark is used to keep constant the speed of an automobile, 
tracking a desired speed reference, compensating disturbances and 
uncertainties related to relief and terrain.The pendulum benchmark consists of a swinging point mass suspended from 
a frictionless pivot by means of a negligible mass rod, while the inverted pendulum 
benchmark is a system similar to the pendulum, but the point 
mass must be equilibrated above the pivot point, which is mounted on an 
one degree of freedom cart that moves over a track through a DC motor.

The magnetic suspension benchmark corresponds to the discrete model of a 
simple eletromagnet-ball system, where a steel ball is levitated in air 
by the action of an electromagnetic force generated by an electromagnet.
The magnetic pointer benchmark is a pointer employed in analogue 
gauges and indicators, whose angular position dynamics is controlled 
by a magnetic field. The 1/4 car suspension benchmark corresponds to the model of a single 
wheel suspension system of a car, {\it i.e.}, the relative motion dynamics 
of a mass springer damp model, which connects the car to one of its wheels.

The computer tape driver benchmark is a computer storage device used to read and write 
data on magnetic tapes. The acrobot benchmark corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}. The high-order system benchmarks correspond to a series of high-order control system model 
generally used as example for order reduction techniques~\cite{CHEN1979389}.
Here, these benchmarks are used to evaluate the proposed control 
synthesis technique under critical conditions, {\it i.e.}, with a large number of parameters 
to be considered.

The continuous stirred tank reactor benchmark describes a linear model for PH dynamics of a PH 
neutralization process of an aqueous solution of sodium acetate with 
hydrochloric acid in a continuous flow stirred-tank reactor. The flexible beam benchmark is a plant 
usually employed in vibration studies; it consists of a flexible metallic structure with piezoceramic actuators and sensors.
The helicopter longitudinal motion benchmark describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.
The USCG cutter tampa heading angle benchmark describes the heading angle 
dynamics of a Coast Guard cutter. The voltage regulator benchmark~\cite{KOKOTOVIC198023} consists 
of a linear model of a synchronous machine connected to an  infinite bus.

The guidance control system benchmark is another high-order system 
model used by Chen et al.~\cite{CHEN1979389}  to evaluate reduction 
techniques. Guidance systems are used to determine the path of an 
autonomous vehicle movement.

The satellite attitude control system benchmark describes the dynamics of a satellite attitude, 
{\it i.e.}, the orientation angles. An attitude control system must 
maintain the desired orientation of a satellite with respect to an 
inertial frame during all the excursion. The springer-mass damper system benchmark 
is classic model for several mechanical systems dynamics. This benchmark describes a mass,
which is fixed to a node by means of a springer and moves under the action of a 
input force, damping, and elastic force.
